---
title: "hw1"
author: "Qiuying Li UNI ql2280"
date: "2/6/2017"
output:
  word_document: default
  pdf_document: default
---
1. Apply the three subset selection methods mentioned above to Credit data set. Plot the RSS as a function of the number of variables for these three methods in the same figure.
```{r}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Desktop/2017 spring/GR 5241/HW/HW1")
credit = read.csv("credit.csv", head = TRUE )
balance = credit$Balance
library(MASS)
library(leaps)
lm3 = regsubsets(balance ~., data = credit)
summary(lm3)$rss
lm4 = regsubsets(balance ~., data = credit,method = "forward")
summary(lm4)$rss
lm5 = regsubsets(balance ~., data = credit,method = "backward")
summary(lm5)$rss
par(mfrow = c(1,1))
plot(summary(lm3)$rss,pch = 0,main = "RSS of three mehods",ylab = "RSS")
points(summary(lm4)$rss,pch = 2)
points(summary(lm5)$rss,pch = 4)
leg.txt = c("exhaustive","forward","backward ")
legend("topright",leg.txt,pch= c(0,2,4))

#points(summary(lm5)$rss,col = "green")
#legend("topright",leg.txt,pch = 1,col= c("red","blue","green"))
```
From the above plot, we could tell that the Rss of three methods are very closed to each other.

2. Each subset selection method results in a set of models. For each approach, choose a single optimal model by using Cp and BIC statistics respectively. Report the optimal models for each approach (i.e. specify the predictors in the optimal model).
```{r cars}
par(mfrow = c(1,3))
plot(lm3,scale = "Cp")
plot(lm4,scale = "Cp")
plot(lm5,scale = "Cp")
summary(lm3,scale = "Cp")
summary(lm4,scale = "Cp")
summary(lm5,scale = "Cp")
plot(lm3,scale = "bic")
plot(lm4,scale = "bic")
plot(lm5,scale = "bic")
summary(lm3,scale = "bic")
summary(lm4,scale = "bic")
summary(lm5,scale = "bic")
```
Problem 3 (PCA, 15 points)
1. For each of the 30 stocks in the Dow Jones Industrial Average, download the closing prices for every trading day from January 1, 2010 to January 1, 2011. Y
```{r}
sym1 = c("MMM","AXP","AAPL","BA","CAT","CVX","CSCO","KO","DD","XOM","GE",
         "GS","HD","IBM","INTC","JNJ","JPM","MCD","MRK","MSFT","NKE","PFE",
         "PG","TRV","UNH","UTX","VZ","V","WMT","DIS")
vec = c("601288","601668","600028")
web = NULL
title = NULL
stock = NULL
for (i in 1:length(vec)){
  web[i] = paste("http://chart.finance.yahoo.com/table.csv?s=", vec[i],".SS&a=0&b=11&c=2017&d=0&e=11&f=2017&g=m&ignore=.csv",sep = "")
  title[i] = paste(vec[i],".csv",sep = "")
  download.file (web[i],title[i],quiet = FALSE)
}
d = c(1:252)
 pr= matrix(d,nrow = 252,ncol = 30)
for( i in 1:length(sym1))
{
  stock = read.csv(title[i],header = T)
  m = stock$ Close
  pr[,i] = m
}
colnames(pr) = sym1
str(pr)
```

2. Perform a PCA on the prices and create the biplot
```{r setup, warning = FALSE}
par(mfrow = c(1,1))
pca1 = princomp(pr, cor = F,center = TRUE,scale. = TRUE)
biplot(pca1)
screeplot(pca1)
```

3.Repeat part 2 with cor=TRUE. This is equivalent to scale each column of the data matrix
```{r, warning = FALSE}
pca2 = princomp(pr, cor = T,center = TRUE,scale. = TRUE)
biplot(pca2)
screeplot(pca2)
```
4. Calculate the return for each stock, and repeat part 3 on the return data. I
```{r}
pr1 = pr[-1,]
pr2 = pr[-252,]
ret1 = pr1 - pr2
pca3= princomp(ret1, cor = T,center = TRUE,scale. = TRUE)
biplot(pca3)
screeplot(pca3)

```